Type cones of $\b{g}$-vector fans

### 2019-02-26 thirdPaper/draft/typeConeAssociahedra.tex
merge

%\tikzlibrary{matrix,quotes,arrows.meta}

@@

\begin{lemma}
The following holds:
\begin{enumerate}[{\rm (a)}]
 \item An object belongs to~$\tc$ if and only if it is projective in~$\cat$.
 \item For any~$T,T'\in\tc$, we have~$\cat(T,\susp T')=0$.
 \item For any~$X\in\cat$ and~$T\in\tc$,~$\cat(X,\susp T)\cong\mathbb{E}(X,T)$.
 \item For any~$X\in\cat$ and~$T\in\tc$,~$\cat(T,X)\cong\mathbb{E}(\susp T,X)$.
 \item The full subcategory~$\susp\tc$ is rigid in~$\cat$.
\end{enumerate}
\end{lemma}

@@

\begin{proof}
Let~$T_1 \overset{t}{\to} T_0$ be a morphism in~$\tc$.
Using the notation of Remark~\ref{remark::equivalence Sigma}, there is an extriangle~$T_1\infl 0\defl \susp T_1 \overset{\eps_{T_1}}{\dashrightarrow}$.
Consider the extriangle~$T_0\overset{g}{\infl} X \overset{h}{\defl} \susp T_1 \overset{t_\ast\eps_{T_1}}{\dashrightarrow}$.
By~\cite[Proposition 3.17]{NakaokaPalu}, there is a commutative diagram of extriangles
\[
\xy
(-7,7)*+{T_1}="2";
(7,7)*+{0}="4";
(21,7)*+{\susp T_1}="6";
(28,7)*+{}="8";
%
(-7,-7)*+{T_0}="12";
(7,-7)*+{X}="14";
(21,-7)*+{\susp T_1}="16";
(28,-7)*+{}="18";
%
(-7,-21)*+{X}="22";
(7,-21)*+{X}="24";
%
(-7,-28)*+{}="32";
(7,-28)*+{}="34";
%
{\ar@{>->} "2";"4"};
{\ar@{->>} "4";"6"};
{\ar@{-->}^{\eps_{T_1}} "6";"8"};
%
{\ar@{>->}_{t'} "2";"12"};
{\ar "4";"14"};
{\ar@{=} "6";"16"};
%
{\ar^{g} "12";"14"};
{\ar^{h} "14";"16"};
{\ar@{-->}^{t_\ast\eps_{T_1}} "16";"18"};
%
{\ar_{g} "12";"22"};
{\ar^{1} "14";"24"};
%
{\ar@{=} "22";"24"};
%
{\ar@{-->}^{h^\ast\eps_{T_1}} "22";"32"};
{\ar@{-->} "24";"34"};
%
{\ar@{}|\circlearrowright "2";"14"};
{\ar@{}|\circlearrowright "4";"16"};
{\ar@{}|\circlearrowright "12";"24"};
\endxy
\]
satisfying~$(t')_\ast\eps_{T_1}=t_\ast\eps_{T_1}$.
We thus have~$t'=t$.
\end{proof}

@@

>>>>

@@

\begin{lemma}\label{lemma::first consequences}
The following holds:
\begin{enumerate}[{\rm (a)}]
 \item An object belongs to~$\tc$ if and only if it is projective in~$\cat$.
 \item For any~$T,T'\in\tc$, we have~$\cat(T,\susp T')=0$.
 \item For any~$X\in\cat$ and~$T\in\tc$,~$\cat(X,\susp T)\cong\mathbb{E}(X,T)$.
 \item For any~$X\in\cat$ and~$T\in\tc$,~$\cat(T,X)\cong\mathbb{E}(\susp T,X)$.
 \item The full subcategory~$\susp\tc$ is rigid in~$\cat$.
\end{enumerate}
\end{lemma}

@@

\begin{proof}
Let~$T_1 \overset{t}{\to} T_0$ be a morphism in~$\tc$.
Using the notation of Remark~\ref{remark::equivalence Sigma}, there is an extriangle~$T_1\infl 0\defl \susp T_1 \overset{\eps_{T_1}}{\dashrightarrow}$.
Consider the extriangle~$T_0\overset{g}{\infl} X \overset{h}{\defl} \susp T_1 \overset{t_\ast\eps_{T_1}}{\dashrightarrow}$.
By~\cite[Proposition 3.17]{NakaokaPalu}, there is a commutative diagram of extriangles
\[
\xy
(-7,7)*+{T_1}="2";
(7,7)*+{0}="4";
(21,7)*+{\susp T_1}="6";
(32,7)*+{}="8";
%
(-7,-7)*+{T_0}="12";
(7,-7)*+{X}="14";
(21,-7)*+{\susp T_1}="16";
(32,-7)*+{}="18";
%
(-7,-21)*+{X}="22";
(7,-21)*+{X}="24";
%
(-7,-32)*+{}="32";
(7,-32)*+{}="34";
%
{\ar@{>->} "2";"4"};
{\ar@{->>} "4";"6"};
{\ar@{-->}^{\eps_{T_1}} "6";"8"};
%
{\ar@{>->}_{t'} "2";"12"};
{\ar "4";"14"};
{\ar@{=} "6";"16"};
%
{\ar^{g} "12";"14"};
{\ar^{h} "14";"16"};
{\ar@{-->}^{t_\ast\eps_{T_1}} "16";"18"};
%
{\ar_{g} "12";"22"};
{\ar^{1} "14";"24"};
%
{\ar@{=} "22";"24"};
%
{\ar@{-->}^{h^\ast\eps_{T_1}} "22";"32"};
{\ar@{-->} "24";"34"};
%
{\ar@{}|\circlearrowright "2";"14"};
{\ar@{}|\circlearrowright "4";"16"};
{\ar@{}|\circlearrowright "12";"24"};
\endxy
\]
satisfying~$(t')_\ast\eps_{T_1}=t_\ast\eps_{T_1}$.
We thus have~$t'=t$.
\end{proof}

@@

\begin{proof}
First note that any injective object belongs to~$\susp \tc$, by Lemma~\ref{lemma::shifts of extriangles}.
Let us prove that the converse holds.
Let~$\susp T \infl X \overset{f}{\defl} Y\overset{\delta}{\dashrightarrow}$ be an extriangle with~$T\in\tc$.
Since~$\cat(-,\susp T)|_\tc = 0$ and~$f$ is~$\tc$-epic, the morphism~$\cat(-,f)_\tc$ is an isomorphism in~$\modt$.
By Proposition~\ref{prop::KRextricat}, there are morphisms~$Y\overset{s}{\to} X$,~$Y\xrightarrow{h}\susp T'$,~$\susp T'\xrightarrow{t} Y$, for some~$T'\in\tc$ satisfying
\[
fs = id_Y + th.
\]
By Lemma~\ref{lemma::first consequences} (e),~$\susp\tc$ is a rigid subcategory so that~$t^\ast\delta=0$.
Equivalently, there is a morphism~$\susp T'\xrightarrow{k} X$ such that~$t=fk$.
We thus have~$f(s-kh)=id_Y$, showing that the extriangle splits.
\end{proof}
